Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-02 paper/ms.tex
paper update

\subsection{Identifying Objects of Interest}
\label{subsec:identifying_ctois}

@@

\subsection{Objects of Interest}
\label{subsec:ctois}

@@

>>>>

\subsection{Identifying Planet Candidates}
\label{subsec:identifying_ctois}

@@

\subsection{Candidate TESS Objects of Interest}
\label{subsec:ctois}

@@

\subsection{Eclipsing binaries, stellar rotation}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{LS_period_vs_color_and_age.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf Time evolution of Lomb-Scargle periodogram peak period versus
    Gaia color.}
    Red stars are on the right, blue stars are on the left.
    Each point on this diagram is a star for which the false alarm
    probability of the most powerful Lomb-Scargle peak is below
    $10^{-15}$.
    Additionally, we required (a) that the membership claim originate
    from \citet{cantat-gaudin_gaia_2018},
    \citet{Kharchenko_et_al_2013}, or \citet{gaia_hr_2018}; and (b)
    that the claimed cluster had an age reported by
    \citet{Kharchenko_et_al_2013}.
	\label{fig:ls_peak_vs_time}
	}
\end{figure}

TODO: describe how this was made.
Figure~\ref{fig:ls_peak_vs_time}.
